Consistency and Fault Tolerance Considerations for the Next Iteration of the DOE Fast Forward Storage and IO Project

### 2014-03-18 paper.tex
added Carlos's ref for Ceph and Gary Grider's comments

Current production HPC IO stack design is unlikely to offer sufficient features
and performance to adequately serve the needs of an extreme scale platform. To
address these limitations, the US Department of Energy commissioned an effort
to develop a design and prototype for an IO stack suitable for the extreme
scale environment. This is a joint effort led by the Intel Lustre team, Los
Alamos National Laboratory, EMC, DDN, and the HDF Group. This team has
developed a specification set~\cite{fastforward:2014:docs} for a future IO
stack to address the identified challenges. The first phase recently completed
with a second phase getting underway. The core focus of the first phase was
basic functionality and design. The second phase will refine this design
incorporating fault recovery and other features missing from the first phase.

@@

Eliminating metadata as a core component of a file system is not new. It has
been explored as part of the Light Weight File Systems
project~\cite{oldfield:lwfs}. In LWFS, the metadata service is explicitly
limited to a user task with the storage layer limited to data
storage/retrieval, authorization, and authentication. This approach proved
workable. Using this hybrid approach is less common and introduces other
issues.

>>>>

Current production HPC IO stack design is unlikely to offer sufficient features
and performance to adequately serve the needs of an extreme scale platform. To
address these limitations, a joint effort between the US Department of Energy's
Office of Advanced Simulation and Computing and Advanced Scientific Computing
Research commissioned an effort to develop a design and prototype for an IO
stack suitable for the extreme scale environment. This is a joint effort led by
Lawrence Livermore National Laboratory, with the DOE Data Management Nexus
leads Rob Ross and Gary Grider as coordinators and contract lead Mark Gary. The
participating labs are LLNL, SNL, LANL, ORNL, PNL, LBNL, and ANL. Additional
industrial partners contracted include the Intel Lustre team, EMC, DDN, and the
HDF Group. This team has developed a specification
set~\cite{fastforward:2014:docs} for a future IO stack to address the
identified challenges. The first phase recently completed with a second phase
getting underway. The core focus of the first phase was basic functionality and
design. Overriding many of the decisions during this and any subsequent phases
is the reality of budgets. Placing GBs of NVRAM on every node, while a
potentially advantageous approach, is not financially feasible. With this in
mind, the second phase will refine this design incorporating fault recovery and
other features missing from the first phase.

@@

Eliminating metadata as a core component of a file system is not new. It has
been explored as part of the Light Weight File Systems
project~\cite{oldfield:lwfs}. In LWFS, the metadata service is explicitly
limited to a user task with the storage layer limited to data
storage/retrieval, authorization, and authentication. This approach proved
workable. Using this hybrid approach is less common~\cite{weil:2006:ceph} and
introduces other issues.
